FTLR proof cases

### 2018-06-18 fully-abstract-comp/ftlr-proof-cases.tex
Fix latex compilation.

\dominique{9-3-2018: the below is a proposed generalisation of the above antireduction lemma  that I expect will hold (based on experience with similar LRs in the past).}
\begin{lemma}[$\lro$ closed under antireduction (generalised previous lemma)]
  \label{lem:lro-anti-red-gen}
  For all $\Phi_S$, $\Phi_S'$, $\Phi_T$, $\Phi_T'$, $j_S,j_T$, $n$, if
  \begin{itemize}
  \item $\Phi_S \nstep[j_S]{\gc} \Phi_S'$
  \item $\Phi_T \nstep[j_T]{} \Phi_T'$
  \item $\npair{(\Phi_S',\Phi_T')} \in \lro$
  \end{itemize}
  then
  \[
    \npair[n+\min(j_S,j_T)]{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  Our two languages are deterministic\dominique{Lemma needed for this, I guess..}, so we have that $\Phi_S \sterm{\ta,\stkb}$ iff $\Phi_S \sterm{\ta,\stkb}$ and $\Phi_T \term$ iff $\Phi_T' \term$.
  It is also easy to show that if $\Phi_S \sterm[i + \min(j_S,j_T)]$, then $\Phi_S' \sterm[i]$ and if $\Phi_T \term[i+\min(j_S,j_T)]$, then $\Phi_T' \term[i]$.
  The result then follows easily by definition of $\lrol$ and $\lror$.
\end{proof}

>>>>

\dominique{9-3-2018: the below is a proposed generalisation of the above antireduction lemma  that I expect will hold (based on experience with similar LRs in the past).}
\begin{lemma}[$\lro$ closed under antireduction (generalised previous lemma)]
  \label{lem:lro-anti-red-gen}
  For all $\Phi_S$, $\Phi_S'$, $\Phi_T$, $\Phi_T'$, $j_S,j_T$, $n$, if
  \begin{itemize}
  \item $\Phi_S \nstep[j_S]{\gc} \Phi_S'$
  \item $\Phi_T \nstep[j_T]{} \Phi_T'$
  \item $\npair{(\Phi_S',\Phi_T')} \in \lro$
  \end{itemize}
  then
  \[
    \npair[n+\min(j_S,j_T)]{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  Our two languages are deterministic\dominique{Lemma needed for this, I guess..}, so we have that $\Phi_S \sterm{\ta,\stkb}$ iff $\Phi_S \sterm{\ta,\stkb}$ and $\Phi_T \term$ iff $\Phi_T' \term$.
  It is also easy to show that if $\Phi_S \sterm{i + \min(j_S,j_T)}$, then $\Phi_S' \sterm{i}$ and if $\Phi_T \term[i+\min(j_S,j_T)]$, then $\Phi_T' \term[i]$.
  The result then follows easily by definition of $\lrol$ and $\lror$.
\end{proof}
